Energy Dependence of Synchrotron X-Ray Rims in Tycho's Supernova Remnant

### 2014-10-24 manuscript/paper-tycho.tex
Paper draft 10/24, faster adaptive errors
Paper draft sent around; adaptive error code steps more quickly
(better criteria for changing step size based on chi-sqr threshold)

@@

\defcitealias{ressler2014}{R14}
\newcommand*{\Chandra}{\textit{Chandra}\ }
\newcommand*{\tsynch}{\tau_{\mt{synch}}}
\newcommand*{\mE}{m_\mt{E}}
\newcommand*{\Ecut}{E_{\mt{cut}}}
\newcommand*{\muG}{\unit{\mu G}}

@@

\begin{abstract}
\note[Aaron]{Modified from AAS abstract - first pass update}
Several young supernova remnants exhibit thin X-ray bright rims of synchrotron
radiation at their forward shocks.  Thin rims have been taken to indicate that
shock-accelerated electrons rapidly cool downstream of the shock, requiring
strong magnetic field amplification.  But, magnetic field damping immediately
behind the shock could produce similarly thin rims.  We measured rim widths
around Tycho's supernova remnant in 5 energy bands using an archival $750
\unit{ks}$ \Chandra observation.  Rims consistently narrow with increasing
energy and are well-described by either loss-limited or magnetically damped
scenarios, hence X-ray rim widths alone cannot discriminate between models.
Loss-limited fits require amplified magnetic fields of $\abt200$--$1000 \muG$
and particle diffusion coefficients $\abt1$--$100\times$ Bohm values,
consistent with prior work on Tycho's SNR, whereas magnetic damping permits
magnetic fields of $\abt 10$--$300 \muG$ and comparatively smaller diffusion
coefficients (typically $\abt 1$--$10$).  Diffusion coefficients, magnetic
field strengths, and magnetic damping lengthscales are somewhat degenerate in
setting observed rim widths and drop-offs.  Although we cannot discriminate
from width measurements alone, a combined study of X-ray and radio profiles may
break the observed degeneracies to confirm or rule out turbulent magnetic field
damping downstream of supernova remnant shocks.
\end{abstract}

@@

% Why Tycho's SNR
To further test these models, we follow \citet{ressler2014} (hereafter,
\citetalias{ressler2014}) by measuring rim widths at multiple energies in the
remnant of Tycho's 1572 supernova (hereafter, Tycho).  Tycho exhibits an
extensive shell of synchrotron-dominated thin rims around its periphery; the
rims show very little thermal emission, consistent with expansion into a low
density ISM \citet{williams2013}.  Tycho, being a nearby galactic SNR, is close
enough that its rims are easily resolved by \textit{Chandra} spatial
resolution. A deep $750 \unit{ks}$ exposure of the entire remnant from 2009
(PI: J. Hughes) also allows us to sample the remnant rims quite finely.
Furthermore, Tycho has been a prime target of study for determining whether
hadrons are being accelerated in historic SNRs \citep[and references
therein]{morlino2012}; understanding the acceleration process will also bear
upon our understanding of CR acceleration in Tycho.
\note[Aaron]{can reword/cut?}

@@

% Transport fundamentals
The energy and space distribution of electrons at a supernova remnant's forward
shock controls the synchrotron rims we see in X-ray and radio.  We assume that
diffusive shock acceleration creates a power-law distribution of electrons with
an exponential cut-off at the forward shock, located at $x = 0$ with $x > 0$
increasing downstream of the shock, given as
$f(E,x=0) = K_0 E^{-s} e^{-E/\Ecut}$.  Here $K_0$ is an arbitrary
normalization, $E$ is electron energy, and the cut-off energy $\Ecut$ is given
below in Section~\ref{sec:diffcoeff}; the spectral index $s$ is taken from
the radio index $\alpha$ as $s = 2\alpha + 1$.

@@

We consider two scenarios for post-shock magnetic field: (1) a constant field
$B(x) = B_0$, corresponding to the loss-limited rim scenario, and (2) an
exponentially damped field of form:
\begin{equation} \label{eq:bdamp}
    B(x) = \left(B_0 - B_{\mt{min}}\right) \exp\left(-x / a_b\right)
           + B_{\mt{min}}
\end{equation}
where $a_b$ is an $e$-folding damping lengthscale, following \citet{pohl2005}.
A typical lengthscale for $a_b$ is $10^{16}$ to $10^{17} \unit{cm}$
\citep{pohl2005}, corresponding to $\abt 0.1$--$1\%$ of Tycho's radius.
Hereafter, we report $a_b$ in units of shock radius $r_s$.

The electron cut-off energy (equation~\eqref{eq:ecut}) depends on the magnetic
field, which varies in a damped model.  For simplicity, we assume that the
shock acceleration process is set by the diffusion at the immediate shock and
so equation~\eqref{eq:ecut} stands as evaluated with magnetic field strength
$B_0$.
\note[Aaron]{Is this correct?  Can try rederiving the expression (particles
penetrate some distance downstream, then back), but I'm not sure if it's even
sensible with diffusion coefficient varying so sharply.}

@@

@@

% TODO final figure should be higher quality, use vector overlay if possible
\begin{figure}
    \centering
    \plotone{figures/f0-snr-inv.png}
    \caption{RGB image of Tycho with region selections overlaid.  Image bands
    are 0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).  Bold region
    labels (1, 16) indicate region selections shown in
    Figures~\ref{fig:spec},~\ref{fig:profiles}.  Filament 1: Regions 1--3,
    filament 2: regions 4--10, filament 3: regions 11-13, filament 4:
    regions 14--17, filament 5, regions 18--20.
    \label{fig:snr}}
\end{figure}
% TODO TODO TODO UPDATE REGION # BOLDING TO MATCH DISPLAYED FILAMENTS ETC

@@

% NOTE must match fig:snr, fig:profiles!
% Keep region numbers updated and consistent.
\begin{figure*}
    \plotone{figures/spec_01.pdf}
    \plotone{figures/spec_16.pdf}
    \caption{Spectra and fits from Regions 1 (top) and 16 (bottom) show varying
    rim morphology and example of rim where 0.7--1 keV peak could not be fit.
    Left: $4.5$--$7 \unit{keV}$ profile with highlighted downstream (blue) and
    upstream (grey) sections.  Intensity in arbitrary units (a.u.).  Middle:
    downstream spectrum with absorbed power law fit; Si and S lines at $1.85$,
    $2.45 \unit{keV}$ are clearly visible.  Right: upstream spectrum with
    absorbed power law fit shows that each region is likely free of thermal
    line
emission.}
    \label{fig:spec}
\end{figure*}

@@

\begin{figure*}%[ht]
    \plotone{figures/prfs_01.pdf}
    \plotone{figures/prfs_16.pdf}
    \caption{Best fit profiles with measured FWHMs demarcated for each energy
        band in Region 1 (top) and Region 16 (bottom).  Energy bands increase
        from left to right.  Data points in red were excluded from profile
        fitting domains as described in text.}
    \label{fig:profiles}
\end{figure*}

@@

% How we ran model fits (itemize knobs, explain energy band mapping, errors,
% fitting procedure
We fit model FWHM predictions given by Equation~ \eqref{eq:model} to our
measured rim widths as a function of energy by varying several physical
parameters: magnetic field strength $B_0$, normalized diffusion coefficient
$\eta_2$, diffusion-energy scaling exponent $\mu$, and minimum field strength
$B_{\mt{min}}$ and lengthscale $a_b$ for a damped magnetic field scenario.  We
mapped each width measurement to the lower energy limit of its energy band;
e.g., $0.7$--$1 \unit{keV}$ is assigned to $0.7 \unit{keV}$ and fitted to model
profile widths at $0.7 \unit{keV}$.  Errors in our least squares fits average
the positive and negative errors on each FWHM measurement.  For an input set of
model parameters, we numerically computed intensity profiles and hence model
FWHMs as detailed in Section~\ref{sec:transport}, and used a
Levenberg-Marquardt fitting routine to identify best fit model parameters
(subject to varied constraints on model parameters in the following paragraph).
To assist the nonlinear fitting, we tabulated model FWHM values on a large grid
of model parameters (primarily $\eta_2$ and $B_0$) and used best-fit grid as
initial guesses for fitting.
% TODO this may be obsoleted if we recompute stuff...  I only computed errors
% on the loss-limited model, and those fits are now out of date too...
Errors on best fit parameters were computed by varying each fit parameter and
obtaining a new best fit model, with one less degree of freedom, to find the
parameter limit such that $\Delta \chi^2 = 1$ for a roughly 1-$\sigma$ error.

@@

% Damped case
For damped magnetic field fits, we held the asymptotic field strength
$B_{\mt{min}}$ inside the remnant constant at $5 \muG$, slightly higher than
typical intergalactic values of $\abt 2$--$3 \muG$ \citep{lyne1989, han2006}.
We fixed $a_b$ at $12$ different values and ran fits with $\eta_2$ and $B_0$
free.  Formally, we do not seek a best fit value of damping length $a_b$, so
our ``best'' damping fits report the value of $a_b$ yielding the smallest
$\chi^2$ value.  Finally, we fixed $\mu = 1$ for all damped fits.

% Variants on our fitting procedure
To better explore the parameter space of model predictions, we also computed
model fits with both $\eta_2 = 1$ and $\mu = 1$ fixed for both scenarios of
constant and damped magnetic field.  We also attempted damping fits with
$B_{\mt{min}} = 2 \muG$, somewhat on the lower end of estimated galactic
magnetic field values.

@@

\begin{table*}
    % Use \tiny for manuscript; \scriptsize for 2-column
    \tiny
    %\scriptsize
    \centering
    \caption{Measured full widths at half max (FWHMs) for all regions.
             \label{tab:fwhms}}
    \input{tab-fwhms.tex}
\end{table*}

% Observations of mE and rim widths and stuff
Measured rim widths decrease with energy in most regions and energy bands.
Although the measurement variation between measurements is quite large, shown
dramatically in the point-wise computed $\mE$ values, the mean rim width
decreases consistently with increasing energy.  Furthermore, mean $\mE$ values
are consistently negative and tend smoothly towards $0$ (weaker
energy-dependence) with increasing energy.

@@

% Explain our approach
We tabulate and plot fitting results for Regions 1 and 16, the same regions
shown in Figures~\ref{fig:spec} and \ref{fig:profiles}.  Although only a small
subset of our regions, qualitative trends in fit parameters were comparable in
most regions; our most salient observations, discussed below, are well
exemplified by Regions 1 and 16.  Best fit results for all regions are
summarized in Tables~\ref{tab:fits-all}, \ref{tabs:fits-all-eta2one}.  In all
tables, we report values of $\chi^2$ rather than $\chi^2_\mt{red}$ to ease
comparison of different fits, as we often manually stepped one or two
parameters that were held constant in fitting.

@@

\begin{figure}
    \centering
    \plotone{figures/full-man_err-prfs_01.pdf}
    \plotone{figures/full-man_err-prfs_16.pdf}
    \caption{Best fit full model rim profile width predictions for Regions 1
        (top) and 16 (bottom) for loss-limited and damped scenarios with
        $\mu = 1$ fixed.  Shaded regions on damped profiles indicate the
        damping ($e$-folding) lengthscale for the magnetic field.  Note that
        radial coordinate ($r$) axes agree in each row (same region), but not
        in each column.
    \label{fig:rims}}
\end{figure}

\begin{figure}
    \centering
    %\epsscale{0.45}  % For manuscript layout only!
    \includegraphics[width=0.23\textwidth]{figures/full-man_err-energywidth-01.pdf}
    \includegraphics[width=0.23\textwidth]{figures/full-man_err-energywidth-16.pdf}
    \caption{Full model width predictions as a function of energy for Regions 1
    (top) and 16 (bottom) with measured data.  Dotted/dashed curves plot
    pure loss-limited fits with varying $\mu$, solid curve plots estimated best
    model fit with moderate damping ($a_b < 0.01$).  Note that ordinate FWHM
    axes do not match and are offset from the origin to better show model
    predictions and data variation.
    \label{fig:fits}}
\end{figure}

% Observations on qualitative trends in fit parameters
% NOTE keep numbers updated.  # of regions "favoring" mu >= 1
% KEEP B0 minimum number updated!!!!!
Loss-limited fits with $\mu \lesssim 1$ generally yield larger parameter values
and errors for both $\eta_2$ and $B_0$, and they are more likely to be
ill-constrained (e.g., $\eta_2 > 10^3$ or $B_0 > 10^3 \muG$).  Fits with $\mu
\gtrsim 1$ generally yield smaller $\chi^2$ values in a majority of regions
($\abt 17$ of $20$), although we do not explore the robustness of this
observation.  Fits for the same data, with varying $\mu$, can yield $\eta_2$
that vary by $1$--$2$ orders of magnitude; Region 16 illustrates this
dramatically (Table~\ref{tab:fits-loss}).

@@

% --------------------------------------------
% Commentary on data, observations, parameters
% Any constraints on parameter values go here
% --------------------------------------------
\subsection{Data and model fit interpretation}

@@

% Move on to address the broader trend in mE, where energy dependence weakens
The observed decrease in $|\mE|$ with increasing energy in data and
(consequently) best model fits may be attributed to diffusion, which weakens
width-energy dependence at higher energies.
As discussed in Section~\ref{sec:energydep}, where advection dominates we
expect $w \sim l_{\mt{ad}} \propto \nu^{-1/2}$ or $\mE \approx -0.5$.  As
diffusion outpaces advection for energies near and above the electron cut-off
energy, $\mE$ will approach values closer to $0$.

The increasing importance of diffusion at X-ray energies matches the
synchrotron spectrum roll-off at X-ray energies as compared to radio
observations; the criterion for synchrotron roll-off, or electron cut-off, is
equivalent to requiring that advective and diffusive lengthscales are
comparable.  Thus, a weakening energy dependence in X-rays is consistent with
prior work.

% Addressing the variability in width measurements
The large variation in filament widths and point-wise computed $\mE$ values
renders our interpretation of $\mE$ more conjectural.  Multiple regions show both
increases and decreases in filament widths between multiple energy bands (e.g.,
Region 9).  But, our averaged results should mitigate this natural measurement
spread.

NOTE that my discussion of diffusion may be masked by damping effects, which
could produce a similar effect.

@@

% TODO THIS IS FOR LOSS LIMITED MODEL ONLY.  Trek through and UPDATE
% Discuss the degeneracy
We now turn to our model fit parameters: magnetic field strength $B_0$ and
scaled diffusion coefficient $\eta_2$.  Our model fit results are poorly
constrained as the parameters $B_0$ and $\eta_2$ may covary without strongly
altering fit quality.  Equations~\eqref{eq:lad} and $\eqref{eq:ldiff}$
illustrate this clearly.  Varying $B_0$ changes both $l_{\mt{ad}}$ and
$l_{\mt{diff}}$ evenly; varying $\eta_2$ (and hence $\eta$) changes only
$l_{\mt{diff}}$, in principle.  But, if diffusion is the primary control on rim
width -- i.e., $l_{\mt{diff}} > l_{\mt{ad}}$ and thus rim width $w \sim
l_{\mt{diff}}$) -- we see that $\eta_2$ and $B_0$ become almost entirely
degenerate.  Ramping up particle diffusion and hence rim widths can be
perfectly counteracted by increasing magnetic fields and forcing electrons to
cool faster, decreasing rim widths.  If advection is the primary control on rim
width (widths narrow rapidly with energy, at $\mE \sim -0.5$), then $\eta_2$
becomes unimportant and the fit is better behaved with effectively one free
parameter.  The degeneracy of $B_0$ and $\eta_2$ is generally stronger for
smaller values of $\mu$, although there appears no clear trend as to when a
particular fit will be ill-constrained.

>>>>

% Customize figures/sizing for 2 column vs. manuscript printout
\usepackage{etoolbox}
\newtoggle{manuscript}
%\toggletrue{manuscript}
\togglefalse{manuscript}

@@

\defcitealias{ressler2014}{R14}
\newcommand*{\Chandra}{\textit{Chandra}\ }
\newcommand*{\tsynch}{\tau_{\mt{synch}}}
\newcommand*{\mE}{m_\mt{E}}
\newcommand*{\Ecut}{E_{\mt{cut}}}
\newcommand*{\Bmin}{B_{\mt{min}}}
\newcommand*{\muG}{\unit{\mu G}}

@@

\begin{abstract}
Several young supernova remnants exhibit thin X-ray bright rims of synchrotron
radiation at their forward shocks.  Thin rims have been taken to indicate that
shock-accelerated electrons rapidly cool downstream of the shock, requiring
strong magnetic field amplification.  But, magnetic field damping immediately
behind the shock could produce similarly thin rims.  We measured rim widths
around Tycho's supernova remnant in 5 energy bands using an archival $750
\unit{ks}$ \Chandra observation.  Rims consistently narrow with increasing
energy and are well-described by either loss-limited or magnetically damped
scenarios, hence X-ray rim widths alone cannot discriminate between models.
Loss-limited fits require amplified magnetic fields of $\abt200$--$1000 \muG$
and particle diffusion coefficients $\abt1$--$100\times$ Bohm values,
consistent with prior work on Tycho's SNR, whereas magnetic damping permits
magnetic fields of $\abt 10$--$300 \muG$ and comparatively smaller diffusion
coefficients (typically $\abt 1$--$10$).  Diffusion coefficients, magnetic
field strengths, and magnetic damping lengthscales are somewhat degenerate in
setting observed rim widths and drop-offs.  Although we cannot discriminate
from width measurements alone, a combined study of X-ray and radio profiles may
break the observed degeneracies to confirm or rule out turbulent magnetic field
damping downstream of supernova remnant shocks.
\end{abstract}

@@

% Why Tycho's SNR
To further test these models, we follow \citet{ressler2014} (hereafter,
\citetalias{ressler2014}) by measuring rim widths at multiple energies in the
remnant of Tycho's 1572 supernova (hereafter, Tycho).  Tycho exhibits an
extensive shell of synchrotron-dominated thin rims around its periphery; the
rims show very little thermal emission, consistent with expansion into a low
density ISM \citet{williams2013}.  Tycho, being a nearby galactic SNR, is close
enough that its rims are easily resolved by \textit{Chandra} spatial
resolution. A deep $750 \unit{ks}$ exposure of the entire remnant from 2009
(PI: J. Hughes) also allows us to sample the remnant rims quite finely.
Furthermore, Tycho has been a prime target of study for determining whether
hadrons are being accelerated in historic SNRs \citep[and references
therein]{morlino2012}; understanding the acceleration process will also bear
upon our understanding of CR acceleration in Tycho.

@@

% Transport fundamentals
The energy and space distribution of electrons at a supernova remnant's forward
shock controls the synchrotron rims we see in X-ray and radio.  We assume that
diffusive shock acceleration creates a power-law distribution of electrons with
an exponential cut-off at the forward shock, located at $x = 0$ with $x > 0$
increasing downstream of the shock, given as
$f(E,x=0) = K_0 E^{-s} e^{-E/\Ecut}$.  Here $K_0$ is an arbitrary
normalization, $E$ is electron energy, and the cut-off energy $\Ecut$ is given
below in Section~\ref{sec:diffcoeff}; the spectral index $s$ is taken from
the radio index $\alpha$ as $s = 2\alpha + 1$.  \citet{zirakashvili2007} have
derived from DSA a slightly different energy spectrum with super-exponential
cut-off $e^{-(p/p_{\mt{cut}})^2}$, which may impact our results; we use a
simple exponential cut-off for simplicity and consistency with
\citetalias{ressler2014}.

@@

We consider two scenarios for post-shock magnetic field: (1) a constant field
$B(x) = B_0$, corresponding to the loss-limited rim scenario, and (2) an
exponentially damped field of form:
\begin{equation} \label{eq:bdamp}
    B(x) = \left(B_0 - \Bmin\right) \exp\left(-x / a_b\right)
           + \Bmin
\end{equation}
where $a_b$ is an $e$-folding damping lengthscale, following \citet{pohl2005}.
A typical lengthscale for $a_b$ is $10^{16}$ to $10^{17} \unit{cm}$
\citep{pohl2005}, corresponding to $\abt 0.1$--$1\%$ of Tycho's radius.
Hereafter, we report $a_b$ in units of shock radius $r_s$.

The electron cut-off energy (equation~\eqref{eq:ecut}) depends on the magnetic
field, which varies in a damped model.  For simplicity, we assume that the
shock acceleration process is set by the diffusion at the immediate shock and
so equation~\eqref{eq:ecut} stands as evaluated with magnetic field strength
$B_0$.
\note[Aaron]{Is this correct?  Can rederive the expression (particles
penetrate some distance downstream, then back), but I'm not sure if it's even
sensible with diffusion coefficient varying so sharply.}

The solutions to equation~\eqref{eq:model} given by \citet{lerche1980,
rettig2012} assume $D(x) B^2(x)$ constant in order to make the equation
semi-analytically tractable.  Although unphysical, we enforce this criterion by
using a modified diffusion coefficient in our calculations following
\citet{rettig2012}, given as:
\begin{equation} \label{eq:ddamp}
    D(E,x) = \frac{\eta C_d E^\mu}{B_0}
             \left[ \frac{\Bmin}{B_0} +
                    \frac{B_0 - \Bmin}{B_0} e^{-x/a_b} \right]^{-2}
\end{equation}
This has the unfortunate effect of strengthening the spatial-dependence of the
diffusion coefficient, which may or may not be physical.
\note[Aaron]{I am not certain whether this should be scaled by $\Bmin$ instead,
will check shortly}

@@

We shall see below that this is qualitatively correct in setting model
predictions of rim shapes (within $\abt a_b$ of the shock front), but our
results are complicated by the increasing importance of energy-dependent
synchrotron losses downstream of the thin rim.  As we use FWHM as a singular
proxy for rim shapes, our procedure is not able to discern the transition in
shape downstream of the damped rim that may impact profile FWHMs, even as
damping controls the main observed rim emission.

@@

% TODO final figure should be higher quality, use vector overlay if possible
\begin{figure}
    \centering
    \iftoggle{manuscript}{
        \includegraphics[width=0.5\textwidth]{figures/f0-snr-inv.png}
    }{
        \plotone{figures/f0-snr-inv.png}
    }
    \caption{RGB image of Tycho with region selections overlaid.  Image bands
    are 0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).  Bold region
    labels (1, 16) indicate region selections shown in
    Figures~\ref{fig:spec},~\ref{fig:profiles}.  Filament 1: Regions 1--3,
    filament 2: regions 4--10, filament 3: regions 11-13, filament 4:
    regions 14--17, filament 5, regions 18--20.
    \label{fig:snr}}
\end{figure}
% TODO TODO TODO UPDATE REGION # BOLDING TO MATCH DISPLAYED FILAMENTS ETC

@@

% NOTE must match fig:snr, fig:profiles!
% Keep region numbers updated and consistent.
\begin{figure*}
    \iftoggle{manuscript}{
        \epsscale{0.7}
    }{}
    \plotone{figures/spec_01.pdf} \\
    \plotone{figures/spec_16.pdf}
    \caption{Spectra and fits from Regions 1 (top) and 16 (bottom) show varying
    rim morphology and example of rim where 0.7--1 keV peak could not be fit.
    Left: $4.5$--$7 \unit{keV}$ profile with highlighted downstream (blue) and
    upstream (grey) sections.  Intensity in arbitrary units (a.u.).  Middle:
    downstream spectrum with absorbed power law fit; Si and S lines at $1.85$,
    $2.45 \unit{keV}$ are clearly visible.  Right: upstream spectrum with
    absorbed power law fit shows that each region is likely free of thermal
    line
emission.}
    \label{fig:spec}
\end{figure*}

@@

\begin{figure*}%[ht]
    \iftoggle{manuscript}{
        \epsscale{1}
    }{}
    \plotone{figures/prfs_01.pdf}
    \plotone{figures/prfs_16.pdf}
    \caption{Best fit profiles with measured FWHMs demarcated for each energy
        band in Region 1 (top) and Region 16 (bottom).  Energy bands increase
        from left to right.  Data points in red were excluded from profile
        fitting domains as described in text.}
    \label{fig:profiles}
\end{figure*}

@@

% How we ran model fits (itemize knobs, explain energy band mapping, errors,
% fitting procedure
We fit model FWHM predictions given by Equation~ \eqref{eq:model} to our
measured rim widths as a function of energy by varying several physical
parameters: magnetic field strength $B_0$, normalized diffusion coefficient
$\eta_2$, diffusion-energy scaling exponent $\mu$, and minimum field strength
$\Bmin$ and lengthscale $a_b$ for a damped magnetic field scenario.  We
mapped each width measurement to the lower energy limit of its energy band;
e.g., $0.7$--$1 \unit{keV}$ is assigned to $0.7 \unit{keV}$ and fitted to model
profile widths at $0.7 \unit{keV}$.  Errors in our least squares fits average
the positive and negative errors on each FWHM measurement.  For an input set of
model parameters, we numerically computed intensity profiles and hence model
FWHMs as detailed in Section~\ref{sec:transport}, and used a
Levenberg-Marquardt fitting routine to identify best fit model parameters
(subject to varied constraints on model parameters in the following paragraph).
To assist the nonlinear fitting, we tabulated model FWHM values on a large grid
of model parameters (primarily $\eta_2$ and $B_0$) and used best-fit grid as
initial guesses for fitting.
% TODO this may be obsoleted if we recompute stuff...  I only computed errors
% on the loss-limited model, and those fits are now out of date too...
Errors on best fit parameters were computed by varying each fit parameter and
obtaining a new best fit model, with one less degree of freedom, to find the
parameter limit such that $\Delta \chi^2 = 1$ for a roughly 1-$\sigma$ error.

@@

% Damped case
For damped magnetic field fits, we held the asymptotic field strength
$\Bmin$ inside the remnant constant at $5 \muG$, slightly higher than
typical intergalactic values of $\abt 2$--$3 \muG$ \citep{lyne1989, han2006}.
We fixed $a_b$ at $12$ different values and ran fits with $\eta_2$ and $B_0$
free.  Formally, we do not seek a best fit value of damping length $a_b$, so
our ``best'' damping fits report the value of $a_b$ yielding the smallest
$\chi^2$ value.  Finally, we fixed $\mu = 1$ for all damped fits.

% Variants on our fitting procedure
To better explore the parameter space of model predictions, we also computed
model fits with both $\eta_2 = 1$ and $\mu = 1$ fixed for both scenarios of
constant and damped magnetic field.  We also attempted damping fits with
$\Bmin = 2 \muG$, somewhat on the lower end of estimated galactic
magnetic field values.

@@

\begin{table*}
    \iftoggle{manuscript}{
        \tiny
    }{
        \scriptsize
    }
    \centering
    \caption{Measured full widths at half max (FWHMs) for all regions.
             \label{tab:fwhms}}
    \input{tab-fwhms.tex}
\end{table*}

% Observations of mE and rim widths and stuff
Measured rim widths decrease with energy in most regions and energy bands.
Although the measurement scatter is quite large, shown dramatically in the
point-wise computed $\mE$ values, the mean rim width decreases consistently
with increasing energy.  Furthermore, mean $\mE$ values are consistently
negative and tend smoothly towards $0$ (weaker energy-dependence) with
increasing energy.

@@

% Explain our approach
We tabulate and plot detailed results for Regions 1 and 16, the same regions
shown in Figures~\ref{fig:spec} and \ref{fig:profiles}.  Although only a small
subset of our regions, qualitative trends in fit parameters were comparable in
most regions; our most salient observations, discussed below, are well
exemplified by Regions 1 and 16.  Best fit results for all regions are
summarized in Tables~\ref{tab:fits-all}, \ref{tab:fits-all-eta2one}.  In all
tables, we report values of $\chi^2$ rather than $\chi^2_\mt{red}$ to ease
comparison of different fits, as we often manually stepped one or two
parameters that were held constant in fitting.

@@

\begin{figure}
    \centering
    \iftoggle{manuscript}{
        \epsscale{0.5}
    }{}
    \plotone{figures/full-man_err-prfs_01.pdf} \\
    \plotone{figures/full-man_err-prfs_16.pdf}
    \caption{Best fit full model rim profile width predictions for Regions 1
        (top) and 16 (bottom) for loss-limited and damped scenarios with
        $\mu = 1$ fixed; profiles are normalized to intensity $1$.  Shaded
        regions on damped profiles indicate the damping ($e$-folding)
        lengthscale for the magnetic field.  Note that radial coordinate ($r$)
        axes agree in each row (same region), but not in each column.
    \label{fig:rims}}
\end{figure}

\begin{figure}
    \centering
    %\epsscale{0.45}  % For manuscript layout only!
    \iftoggle{manuscript}{
        \includegraphics[width=0.46\textwidth]{figures/full-man_err-energywidth-01.pdf}
        \includegraphics[width=0.46\textwidth]{figures/full-man_err-energywidth-16.pdf}
    }{
        \includegraphics[width=0.23\textwidth]{figures/full-man_err-energywidth-01.pdf}
        \includegraphics[width=0.23\textwidth]{figures/full-man_err-energywidth-16.pdf}
    }
    \caption{Full model width predictions as a function of energy for Regions 1
    (top) and 16 (bottom) with measured data.  Dotted/dashed curves plot
    pure loss-limited fits with varying $\mu$, solid curve plots estimated best
    model fit with moderate damping ($a_b < 0.01$).  Note that ordinate FWHM
    axes do not match and are offset from the origin to better show model
    predictions and data variation.
    \label{fig:fits}}
\end{figure}

% Observations on qualitative trends in fit parameters
% NOTE keep numbers updated.  # of regions "favoring" mu >= 1
% KEEP B0 minimum number updated!!!!!
Loss-limited fits with $\mu \lesssim 1$ generally yield larger parameter values
and errors for both $\eta_2$ and $B_0$, and they are more likely to be
ill-constrained (e.g., $\eta_2 > 10^3$ or $B_0 > 10^3 \muG$).  Fits with $\mu
\gtrsim 1$ yield smaller $\chi^2$ values in a majority of regions ($\abt 17$ of
$20$), although we do not explore the robustness of this observation.  Fits to
the same data with varying $\mu$ can yield $\eta_2$ varying by $1$--$2$ orders
of magnitude; Region 16 illustrates this dramatically
(Table~\ref{tab:fits-loss}).

@@

Here we first explore trends in our data and best-fit diffusion and magnetic
fields.  We then discuss discrimination of the loss-limited and damping models
(i.e., our ability to favor or constrain a finite value of $a_b$), and possible
paths forward to better constrain our model parameters.

% --------------------------------------------
% Commentary on data, observations, parameters
% Tycho distance estimates, maybe compression ratio stuff...
% Any constraints on parameter values go here
% --------------------------------------------
\subsection{Data and model fit interpretation}

@@

% First address the broad trend of leveling energy dependence in mE)
We suggest that our observed decrease in $|\mE|$ with increasing energy is
caused by diffusion, which weakens width-energy dependence at higher energies.
The photon energy at which advection and diffusion are comparably important
($l_{\mt{ad}} = l_{\mt{diff}}$) is exactly the synchrotron roll-off energy,
$\abt 0.3 \unit{keV}$ in Tycho \citep{hwang2002}.  Then we expect diffusion to
begin overtaking advection and depress $\mE$ towards $0$ in soft X-rays, as
opposed to $\mE \abt -0.5$ expected when advection is important
(Section~\ref{sec:energydep}).  A decrease in $|\mE|$ is then reassuringly
consistent with the framework of diffusive shock acceleration.

% This conclusion is based strictly on our measurements.
% Our transport model hard-codes this width leveling through \Ecut

% Discuss variability in width measurements
The large scatter in filament widths and hence point-wise computed $\mE$ values
(Table~\ref{tab:fwhms}) does relegate our interpretation of $\mE$ to conjecture.
Multiple regions show both increases and decreases in filament widths between
energy bands, and we have seen that diffusion ($\eta_2$) is poorly constrained
by our fit results.  Our averaged results should mitigate this natural
measurement spread, however.

% Can damping explain stuff?
The next question is whether damping may also produce this effect, independent
of assumptions on the shock acceleration process.  Conceptually, if damping
controls rim widths past the cut-off energy, $|\mE|$ may slightly decrease or
even increase as rims transition from being damping controlled to being
diffusion loss-limited.  If damping is only important well below the cut-off
energy, then we may see an increase in $|\mE|$ as advection becomes important.
Although magnetic damping is able to fit observed rim widths, our model assumes
diffusive shock acceleration in computing $\Ecut$ and hence we may not use our
model fits to assess whether magnetic damping can independently account for
decreasing $|\mE|$.

% Curious effects of damping competing with other things
Downstream energy losses in a well damped field (multiple $e$-folding
lengths ($a_b$) downstream) may also introduce energy dependence in rim widths.
Sufficiently energetic electrons will radiate and cool within the damping
length $a_b$, but lower energy electrons will perceive a relatively constant
field $\abt \Bmin$ downstream of the shock.  Synchrotron losses will
``sieve'' out higher energy electrons as in the loss-limited model, and
observed rim widths, if larger than $a_b$, may be somewhat loss-limited at low
energies, well-confined by damping at moderate energies, then diffusion (or
cut-off spectrum) limited at the highest energies.

We revisit the effects of damping further below.  The observation of decreasing
$|\mE|$, however, remains consistent with and expected from the theory of
diffusive shock acceleration.

@@

% Discuss degeneracy in loss-limited and damped models both
We now turn to our model fit parameters: magnetic field strength $B_0$ and
scaled diffusion coefficient $\eta_2$.  Our loss-limited fit results are poorly
constrained as $B_0$ and $\eta_2$ may covary without strongly altering fit
quality.  If diffusion is the primary control on rim width -- i.e.,
$l_{\mt{diff}} > l_{\mt{ad}}$ and thus rim width $w \sim l_{\mt{diff}}$) --
then $\eta_2$ and $B_0$ become degenerate as the product $\eta^{1/2}
B_0^{-3/2}$ exerts most control on rim width $w$.  If advection is the primary
control on rim width (widths narrow rapidly with energy, at $\mE \sim -0.5$),
then $\eta_2 \ll 1$ becomes unimportant and the fit is better behaved with
effectively one free parameter.  The degeneracy of $B_0$ and $\eta_2$ is
stronger for smaller values of $\mu$, although there appears no clear trend as
to when a particular fit will be ill-constrained.

In the damped model, a similar degeneracy is present but modified somewhat by
the presence of damping.  For small values of $a_b$ (strong damping), increased
diffusion $\eta_2$ can cause rim widths to \emph{narrow}, contrary to
intuition; $B_0$ and $\eta_2$ generally covary in controlling rim widths, but
the relationship is now less clear.  Speculatively, the opposition to
downstream flow may be tied to the spatial variation of the diffusion
coefficient, which gives rise to an additional term $-(\ptl D(x) / \ptl x)
(\ptl f/\ptl x)$ that opposes downstream flow in equation~\eqref{eq:model}.

% NOTE some of this discussion of parameter values could go
% into results instead.

% B0 lower bounds, etc. in loss-limited model
In our loss-limited model fits, the minimum magnetic field strength we observe
throughout the remnant, within stated errors, is $B_0 = 179 \muG$.  The minimum
values of $B_0$ for each filament (1--5) are $179$, $254$, $287$, $458$, and
$243 \muG$.  We observe the smallest $B_0$ values for $\eta_2$ approaching $0$
and $\mu = 2$; intuitively, $\mu = 2$ gives stronger diffusion at higher
energies ($>2\unit{keV}$) where it is most ``needed'' to reproduce the leveling
off of filament widths and so $\mu = 2$ permits a smaller best-fit $\eta_2$ and
hence smaller $B_0$.  Furthermore, when $\eta_2 = 1$ is fixed we find that
$B_0$ is well-constrained in the loss-limited model, falling strictly between
$180$--$500 \muG$ (Table~\ref{tab:fits-all-eta2one}).  In this scenario the
range of $B_0$ values is directly correlated to the observed range of rim
widths.  Our minimum loss-limited values of $B_0$ are consistent with prior
estimates of $\abt 200$--$300 \muG$ for primarily advective transport
\citep{volk2005, parizot2006, morlino2012}.  If loss-limited, Tycho's rims
require strong magnetic field amplification -- at least $\abt 100\times$ the
typical galactic field values of $\abt 2$--$3 \muG$, versus the expected
$4\times$ amplification from a strong shock with compression ratio $r=4$.
